\cvsection{Publications}

As of \today\ I have 53 submitted or accepted publications with a total of 1144 citations (NASA/ADS).\\

My $h$-index is 14, which places me better than the top 5\% of all Australian astronomers within 0--5 years post-PhD (Pimbblet 2011, PASA, 28, 140), despite currently being $\approx$3 years post-PhD.

\vspace{2em}

\cvsubsection{First-author Publications (9)}

\begin{cvpublications}
\cvpublication{\href{http://adsabs.harvard.edu/abs/2016arXiv160902914C}{The RAVE-on catalog of stellar atmospheric parameters and chemical abundances for chemo-dynamic studies in the Gaia era}}{Casey, Andrew R.; Hawkins, Keith; Hogg, David W.; Ness, Melissa; Walter-Rix, Hans; Kordopatis, Georges; Kunder, Andrea; Steinmetz, Matthias; Koposov, Sergey; Enke, Harry et al.}{2016}{1}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stw1512}{The Gaia-ESO Survey: revisiting the Li-rich giant problem}}{Casey, A. R.; Ruchti, G.; Masseron, T.; Randich, S.; Gilmore, G.; Lind, K.; Kennedy, G. M.; Koposov, S. E.; Hourihane, A.; Franciosini, E. et al.}{2016}{2}

\cvpublication{\href{http://adsabs.harvard.edu/abs/2016arXiv160303040C}{The Cannon 2: A data-driven model of stellar spectra for detailed chemical abundance analyses}}{Casey, Andrew R.; Hogg, David W.; Ness, Melissa; Rix, Hans-Walter; Ho, Anna Q Y; Gilmore, Gerry}{2016}{3}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.3847/0067-0049/223/1/8}{sick: The Spectroscopic Inference Crank}}{Casey, Andrew R.}{2016}{4}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/0004-637X/809/2/110}{Chemistry of the Most Metal-poor Stars in the Bulge and the z  10 Universe}}{Casey, Andrew R.; Schlaufman, Kevin C.}{2015}{5}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stu1031}{The Aquarius comoving group is not a disrupted classical globular cluster}}{Casey, A. R.; Keller, S. C.; Alves-Brito, A.; Frebel, A.; Da Costa, G.; Karakas, A.; Yong, D.; Schlaufman, K. C.; Jacobson, H. R.; Yu, Q. et al.}{2014}{6}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/0004-637X/784/1/19}{Hunting the Parent of the Orphan Stream. II. The First High-resolution Spectroscopic Study}}{Casey, Andrew R.; Keller, Stefan C.; Da Costa, Gary; Frebel, Anna; Maunder, Elizabeth}{2014}{7}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/0004-637X/764/1/39}{Hunting the Parent of the Orphan Stream: Identifying Stream Members from Low-resolution Spectroscopy}}{Casey, Andrew R.; Da Costa, Gary; Keller, Stefan C.; Maunder, Elizabeth}{2013}{8}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/0004-6256/143/4/88}{Kinematics and Chemistry of Halo Substructures: The Vicinity of the Virgo Overdensity}}{Casey, Andrew R.; Keller, Stefan C.; Da Costa, Gary}{2012}{9}
	
\end{cvpublications}

\vspace{2em}

\cvsubsection{Second-author Publications (6)}

\begin{cvpublications}
\cvpublication{\href{http://adsabs.harvard.edu/abs/10.3847/1538-4357/833/2/262}{Chemical Tagging Can Work: Identification of Stellar Phase-space Structures Purely by Chemical-abundance Similarity}}{Hogg, David W.; Casey, Andrew R.; Ness, Melissa; Rix, Hans-Walter; Foreman-Mackey, Daniel; Hasselquist, Sten; Ho, Anna Y. Q.; Holtzman, Jon A.; Majewski, Steven R.; Martell, Sarah L. et al.}{2016}{1}

\cvpublication{\href{http://adsabs.harvard.edu/abs/2015arXiv151103930H}{Extremely metal-poor stars from the cosmic dawn in the bulge of the Milky Way}}{Howes, L. M.; Casey, A. R.; Asplund, M.; Keller, S. C.; Yong, D.; Nataf, D. M.; Poleski, R.; Lind, K.; Kobayashi, C.; Owen, C. I. et al.}{2015}{2}

\cvpublication{\href{http://adsabs.harvard.edu/abs/2015arXiv151103428F}{The Mass Distribution of Population III Stars}}{Fraser, M.; Casey, A. R.; Gilmore, G.; Heger, A.; Chan, C.}{2015}{3}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/0004-637X/811/1/62}{Kinematics and Chemistry of Recently Discovered Reticulum 2 and Horologium 1 Dwarf Galaxies}}{Koposov, Sergey E.; Casey, Andrew R.; Belokurov, Vasily; Lewis, James R.; Gilmore, Gerard; Worley, Clare; Hourihane, Anna; Randich, S.; Bensby, T.; Bragaglia, A. et al.}{2015}{4}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/0004-637X/797/1/13}{The Best and Brightest Metal-poor Stars}}{Schlaufman, Kevin C.; Casey, Andrew R.}{2014}{5}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/0004-637X/769/1/57}{Deriving Stellar Effective Temperatures of Metal-poor Stars with the Excitation Potential Method}}{Frebel, Anna; Casey, Andrew R.; Jacobson, Heather R.; Yu, Qinsi}{2013}{6}

\end{cvpublications}

\clearpage

\cvsubsection{$N$th-author Publications (37)}

\begin{cvpublications}
\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stw2835}{The GALAH survey: observational overview and Gaia DR1 companion}}{Martell, S. L.; Sharma, S.; Buder, S.; Duong, L.; Schlesinger, K. J.; Simpson, J.; Lind, K.; Ness, M.; Marshall, J. P.; Asplund, M. et al.}{2017}{1}

\cvpublication{\href{http://adsabs.harvard.edu/abs/2017arXiv170201109T}{The $Gaia$-ESO Survey: the inner disk intermediate-age open cluster NGC 6802}}{Tang, B.; Geisler, D.; Friel, E.; Villanova, S.; Smiljanic, R.; Casey, A. R.; Randich, S.; Magrini, L.; San Roman, I.; Munoz, C. et al.}{2017}{2}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1038/s41550-017-0042}{The language of exoplanet ranking metrics needs to change}}{Tasker, Elizabeth; Tan, Joshua; Heng, Kevin; Kane, Stephen; Spiegel, David; Brasser, Ramon; Casey, Andrew; Desch, Steven; Dorn, Caroline; Hernlund, John et al.}{2017}{3}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stw2064}{The GALAH survey: the data reduction pipeline}}{Kos, Janez; Lin, Jane; Zwitter, Tomaz; Zerjal, Maruska; Sharma, Sanjib; Bland-Hawthorn, Joss; Asplund, Martin; Casey, Andrew R.; De Silva, Gayandhi M.; Freeman, Ken C. et al.}{2017}{4}

\cvpublication{\href{http://adsabs.harvard.edu/abs/2017arXiv170101444W}{On the Run: mapping the escape speed across the Galaxy with SDSS}}{Williams, Angus A.; Belokurov, Vasily; Casey, Andrew R.; Evans, N. Wyn}{2017}{5}

\cvpublication{\href{http://adsabs.harvard.edu/abs/2017arXiv170107829N}{Galactic Doppelganger: The chemical similarity among field stars and among stars with a common birth origin}}{Ness, M.; Rix, H-W.; Hogg, David W.; Casey, A. R.; Holtzman, J.; Fouesneau, M.; Zasowski, G.; Geisler, D.; Shetrone, M.; Minniti, D. et al.}{2017}{6}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stx047}{Sc and neutron-capture abundances in Galactic low- and high- field halo stars}}{Fishlock, C. K.; Yong, D.; Karakas, A. I.; Alves-Brito, A.; Melendez, J.; Nissen, P. E.; Kobayashi, C.; Casey, A. R.}{2017}{7}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201629202}{3D NLTE analysis of the most iron-deficient star, SMSS0313-6708}}{Nordlander, T.; Amarsi, A. M.; Lind, K.; Asplund, M.; Barklem, P. S.; Casey, A. R.; Collet, R.; Leenaarts, J.}{2017}{8}

\cvpublication{\href{http://adsabs.harvard.edu/abs/2017arXiv170103741S}{The Gaia-ESO Survey: Structural and dynamical properties of the young cluster Chamaeleon I}}{Sacco, G. G.; Spina, L.; Randich, S.; Palla, F.; Parker, R. J.; Jeffries, R. D.; Jackson, R.; Meyer, M. R.; Mapelli, M.; Lanzafame, A. C. et al.}{2017}{9}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stw2458}{The Gaia-ESO Survey: lithium depletion in the Gamma Velorum cluster and inflated radii in low-mass pre-main-sequence stars}}{Jeffries, R. D.; Jackson, R. J.; Franciosini, E.; Randich, S.; Barrado, D.; Frasca, A.; Klutsch, A.; Lanzafame, A. C.; Prisinzano, L.; Sacco, G. G. et al.}{2017}{10}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201629450}{The Gaia-ESO Survey: Calibration strategy}}{Pancino, E.; Lardo, C.; Altavilla, G.; Marinoni, S.; Ragaini, S.; Cocozza, G.; Bellazzini, M.; Sabbi, E.; Zoccali, M.; Donati, P. et al.}{2017}{11}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.3847/0004-637X/833/1/21}{Observational Constraints on First-Star Nucleosynthesis. II. Spectroscopy of an Ultra metal-poor CEMP-no Star}}{Placco, Vinicius M.; Frebel, Anna; Beers, Timothy C.; Yoon, Jinmi; Chiti, Anirudh; Heger, Alexander; Chan, Conrad; Casey, Andrew R.; Christlieb, Norbert}{2016}{12}

\cvpublication{\href{http://adsabs.harvard.edu/abs/2016arXiv161202242T}{The Galah Survey: Classification and diagnostics with t-SNE reduction of spectral information}}{Traven, G.; Matijevic, G.; Zwitter, T.; Zerjal, M.; Kos, J.; Asplund, M.; Bland-Hawthorn, J.; Casey, A. R.; De Silva, G.; Freeman, K. et al.}{2016}{13}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.3847/2041-8205/832/1/L3}{Chemical Diversity in the Ultra-faint Dwarf Galaxy Tucana II}}{Ji, Alexander P.; Frebel, Anna; Ezzeddine, Rana; Casey, Andrew R.}{2016}{14}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201629091}{Stellar twins determine the distance of the Pleiades}}{Madler, Thomas; Jofre, Paula; Gilmore, Gerard; Clare Worley, C.; Soubiran, Caroline; Blanco-Cuaresma, Sergi; Hawkins, Keith; Casey, Andrew R.}{2016}{15}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201528010}{The Gaia-ESO Survey: Hydrogen lines in red giants directly trace stellar mass}}{Bergemann, Maria; Serenelli, Aldo; Schonrich, Ralph; Ruchti, Greg; Korn, Andreas; Hekker, Saskia; Kovalev, Mikhail; Mashonkina, Lyudmila; Gilmore, Gerry; Randich, Sofia et al.}{2016}{16}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stw1217}{The Gaia-ESO Survey: pre-main-sequence stars in the young open cluster NGC 3293}}{Delgado, A. J.; Sampedro, L.; Alfaro, E. J.; Costado, M. T.; Yun, J. L.; Frasca, A.; Lanzafame, A. C.; Drew, J. E.; Eisloffel, J.; Blomme, R. et al.}{2016}{17}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stw1004}{The EMBLA survey - metal-poor stars in the Galactic bulge}}{Howes, Louise M.; Asplund, Martin; Keller, Stefan C.; Casey, Andrew R.; Yong, David; Lind, Karin; Frebel, Anna; Hays, Austin; Alves-Brito, Alan; Bessell, Michael S. et al.}{2016}{18}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stw1011}{The Gaia-ESO Survey: the selection function of the Milky Way field stars}}{Stonkute, E.; Koposov, S. E.; Howes, L. M.; Feltzing, S.; Worley, C. C.; Gilmore, G.; Ruchti, G. R.; Kordopatis, G.; Randich, S.; Zwitter, T. et al.}{2016}{19}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.3847/2041-8205/824/2/L29}{The Gaia-ESO Survey: Metal-rich Bananas in the Bulge}}{Williams, Angus A.; Evans, N. W.; Molloy, Matthew; Kordopatis, Georges; Smith, M. C.; Shen, J.; Gilmore, G.; Randich, S.; Bensby, T.; Francois, P. et al.}{2016}{20}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201628169}{Gaia-ESO Survey: Gas dynamics in the Carina nebula through optical emission lines}}{Damiani, F.; Bonito, R.; Magrini, L.; Prisinzano, L.; Mapelli, M.; Micela, G.; Kalari, V.; Maiz Apellaniz, J.; Gilmore, G.; Randich, S. et al.}{2016}{21}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201527654}{The Gaia-ESO Survey: Probes of the inner disk abundance gradient}}{Jacobson, H. R.; Friel, E. D.; Jilkova, L.; Magrini, L.; Bragaglia, A.; Vallenari, A.; Tosi, M.; Randich, S.; Donati, P.; Cantat-Gaudin, T. et al.}{2016}{22}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201628526}{The Gaia-ESO Survey: Inhibited extra mixing in two giants of the open cluster Trumpler 20?}}{Smiljanic, R.; Franciosini, E.; Randich, S.; Magrini, L.; Bragaglia, A.; Pasquini, L.; Vallenari, A.; Tautvaisiene, G.; Biazzo, K.; Frasca, A. et al.}{2016}{23}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201528014}{The Gaia-ESO Survey: Sodium and aluminium abundances in giants and dwarfs. Implications for stellar and Galactic chemical evolution}}{Smiljanic, R.; Romano, D.; Bragaglia, A.; Donati, P.; Magrini, L.; Friel, E.; Jacobson, H.; Randich, S.; Ventura, P.; Lind, K. et al.}{2016}{24}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201628336}{The Gaia-ESO Survey: A lithium-rotation connection at 5 Myr?}}{Bouvier, J.; Lanzafame, A. C.; Venuti, L.; Klutsch, A.; Jeffries, R.; Frasca, A.; Moraux, E.; Biazzo, K.; Messina, S.; Micela, G. et al.}{2016}{25}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stv1724}{Climbing the cosmic ladder with stellar twins}}{Jofre, P.; Madler, T.; Gilmore, G.; Casey, A. R.; Soubiran, C.; Worley, C.}{2015}{26}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201526305}{The Gaia-ESO Survey: Insights into the inner-disc evolution from open clusters}}{Magrini, L.; Randich, S.; Donati, P.; Bragaglia, A.; Adibekyan, V.; Romano, D.; Smiljanic, R.; Blanco-Cuaresma, S.; Tautvaisiene, G.; Friel, E. et al.}{2015}{27}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1117/1.JATIS.1.3.035002}{First light results from the High Efficiency and Resolution Multi-Element Spectrograph at the Anglo-Australian Telescope}}{Sheinis, Andrew; Anguiano, Borja; Asplund, Martin; Bacigalupo, Carlos; Barden, Sam; Birchall, Michael; Bland-Hawthorn, Joss; Brzeski, Jurek; Cannon, Russell; Carollo, Daniela et al.}{2015}{28}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/0004-637X/807/2/171}{High-Resolution Spectroscopic Study of Extremely Metal-Poor Star Candidates from the SkyMapper Survey}}{Jacobson, Heather R.; Keller, Stefan; Frebel, Anna; Casey, Andrew R.; Asplund, Martin; Bessell, Michael S.; Da Costa, Gary S.; Lind, Karin; Marino, Anna F.; Norris, John E. et al.}{2015}{29}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/2041-8205/806/1/L16}{Nucleosynthesis in a Primordial Supernova: Carbon and Oxygen Abundances in SMSS J031300.36-670839.3}}{Bessell, Michael S.; Collet, Remo; Keller, Stefan C.; Frebel, Anna; Heger, Alexander; Casey, Andrew R.; Masseron, Thomas; Asplund, Martin; Jacobson, Heather R.; Lind, Karin et al.}{2015}{30}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stv327}{The GALAH survey: scientific motivation}}{De Silva, G. M.; Freeman, K. C.; Bland-Hawthorn, J.; Martell, S.; de Boer, E. Wylie; Asplund, M.; Keller, S.; Sharma, S.; Zucker, D. B.; Zwitter, T. et al.}{2015}{31}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stu2144}{NGC 6522: a typical globular cluster in the Galactic bulge without signatures of rapidly rotating Population III stars}}{Ness, Melissa; Asplund, Martin; Casey, Andrew R.}{2014}{32}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1093/mnras/stu1991}{The Gaia-ESO Survey: the most metal-poor stars in the Galactic bulge}}{Howes, L. M.; Asplund, M.; Casey, A. R.; Keller, S. C.; Yong, D.; Gilmore, G.; Lind, K.; Worley, C.; Bessell, M. S.; Casagrande, L. et al.}{2014}{33}

\cvpublication{\href{http://adsabs.harvard.edu/abs/2014arXiv1402.1517K}{A single low-energy, iron-poor supernova as the source of metals in the star SMSS J031300.36-670839.3}}{Keller, S. C.; Bessell, M. S.; Frebel, A.; Casey, A. R.; Asplund, M.; Jacobson, H. R.; Lind, K.; Norris, J. E.; Yong, D.; Heger, A. et al.}{2014}{34}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1051/0004-6361/201322068}{Astropy: A community Python package for astronomy}}{Astropy Collaboration; Robitaille, Thomas P.; Tollerud, Erik J.; Greenfield, Perry; Droettboom, Michael; Bray, Erik; Aldcroft, Tom; Davis, Matt; Ginsburg, Adam; Price-Whelan, Adrian M. et al.}{2013}{35}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/0004-637X/771/1/39}{The 300 km s<SUP>-1</SUP> Stellar Stream near Segue 1: Insights from High-resolution Spectroscopy of Its Brightest Star}}{Frebel, Anna; Lunnan, Ragnhild; Casey, Andrew R.; Norris, John E.; Wyse, Rosemary F. G.; Gilmore, Gerard}{2013}{36}

\cvpublication{\href{http://adsabs.harvard.edu/abs/10.1088/0004-637X/733/2/75}{The Extragalactic Distance Scale without Cepheids. IV.}}{Hislop, Lachlan; Mould, Jeremy; Schmidt, Brian; Bessell, Michael S.; Da Costa, Gary; Francis, Paul; Keller, Stefan; Tisserand, Patrick; Rapoport, Sharon; Casey, Andy}{2011}{37}

\end{cvpublications}

%\begin{cvpublications}
%	\cvpublication{title}{authors}{journal}{year}
%\end{cvpublications}
